---
title: 'FIT5145 Seminar Activity: Scrape it, fix it, join it'
output: html_document
date: "2026-08-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FIT5145 Seminar Activity

### Wrangling Capstone: scrape it, fix it, join it

```{r}
library(tidyverse)
library(rvest)
```

#### 1. Web scraping  - Week 3 applied clas material code, unchanged
```{r}
t20i_url  <- "https://en.wikipedia.org/wiki/ICC_Men%27s_T20I_Team_Rankings"
t20i_page <- read_html(t20i_url)
t20i      <- t20i_page %>% html_element("table.sortable") %>% html_table()

colnames(t20i) <- c("Team", "Matches", "Points", "Rating")
t20i <- t20i[-102, ]      # remove the footnote row
t20i <- t20i[1:3, ]      # keep the top 3 teams
t20i$Rating <- as.integer(t20i$Rating)
t20i
```

#### 2. READ THE MESSY CSV, team_runs_messy.csv
```{r}
runs <- read.csv("team_runs_messy.csv")
  
runs
```

#### 3. Convert the structure of the runs dataset
Hint: use 'gather' function
```{r}
runs_long <- runs %>% gather(key="year", value = "runs")
  
runs_long
```
#### 4. Normalise the join key
Hint: use 'recode' function
```{r}
runs_long <- ???
  
runs_long
```

#### 5. COMBINE: JOIN
##### Bring each team's current Rating alongside its yearly runs.
Hint: use 'join' function
```{r}
final <- runs_long 
  
final
```








